Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Bundles.

>>>>

We implemented meek as a Tor pluggable transport~\cite{pt}
and built experimental releases of the Tor Browser Bundle featuring meek.
The browser bundle includes Tor and a version of Firefox
called Tor Browser that is patched to defend against application-layer identity leaks.
Users need to download and run the bundle and select meek from the list of transports,
and then a browser window appears,
configured to use meek for circumvention and Tor for anonymity.
We announced our prototype bundles on Tor development mailing lists,
and from there they were picked up by Tor Weekly News on the Tor blog.
